Construction of Chebyshev nets with singularities

### 2017-07-07 Article.tex
Suppression de la section régularité

\modif{Théorème final}
\begin{theorem}[Existence of a smooth Chebyshev net out of a finite
    number of balls]\label{thm:existence-cheb-net}
  Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$ satisfying
\begin{equation} \label{eq:cond-thm}
  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
\end{equation}
where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
Then, there exists a finite number of balls $(\B_i)_{1\leq i\leq \N}$
with an arbitrary small radius $\varepsilon$ such that
$M\setminus\bigcup_{1\leq i\leq \N}\B_i$ admits a smooth Chebyshev
net. \modif{Ajouter estimation sur $\N$.}
\end{theorem}

@@

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2full}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be two smooth
curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega:D\to(0,\pi)$ verifying the boundary conditions
\eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula
\eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the
unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a smooth Chebyshev net on $\Omega$ with angles
$0<\omega<\pi$.
\end{theorem}

In order to prove Theorem \ref{thm2full}, we proceed along the following plan. In Section \ref{subsec:constr-param}, given the two curves $\gamma_u$ and $\gamma_v$ on $\surf$ and the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves, we first construct the candidate Chebyshev net $\varphi=\I(\gamma,\omega):D\to\surf$. We then show that whenever $\varphi$ satisfies the integrability condition \eqref{eq:cond-integr}, this mapping also satisfies \eqref{eq:cheb-def-c3} under suitable regularity conditions.  In Section \ref{subsec:exist-pt-fixe}, we view the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)$, as a fixed-point problem on $\omega$. We show existence and uniqueness of the solution to this fixed-point equation for the curves $\gamma_u$ and $\gamma_v\big|_{[0,L_0]}:[0,L_0]\to\surf$, where $L_0\in(0,L_v]$ is a constant depending on the $C^0$-norm of the geodesic curvatures of $\gamma_u$ and $\gamma_v$. This result is called ``local existence'' in what follows. We finally extend this result to the curves $\gamma_u$ and $\gamma_v$ of arbitrary length, in the spirit of the Cauchy--Lipschitz theorem.

\subsection{Functional spaces and statement of the main result}\label{sec:norms}

We now turn to the regularity required on the curves $\gamma_u$ and $\gamma_v$ and on the angle distribution $\omega$. In what follows, we define the spaces in which the curves, parametrizations and angles are constructed.  %When no confusion is possible, the mention of $L$, $L_u$ and $L_v$ will be dropped in the following notations for the sake of brevity.
Recall that
\begin{equation*}
  D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+.
\end{equation*}
Let $k\in\EN$ and $L\in(0,L_v]$. We consider the space $C^{k+2}([0,L],\surf)$ of curves $\gamma$ with general parametrizations on $\surf$ and such that the geodesic curvature of $\gamma$ has $C^{k}$-regularity. % The space $W^{k+2,p}$, endowed with the norm
% \begin{equation}\label{normphi}
%   \|\gamma\|_{W^{k+2,p}} = |\gamma(0)|+|\gamma'(0)| + \|\gamma''\|_{W^{k,p}([0,L])},
% \end{equation}
% is a Banach space.
We define $\Gamma^{k+2}([0,L])$ to be the closed subset of $C^{k+2}([0,L],\surf)$ formed by arc-length parametrized curves:
\begin{equation*}  
  \Gamma^{k+2}([0,L]) = \Big\{\gamma \in C^{k+2}([0,L], \surf) \text{ s.t. } \forall s\in[0,L],~ |\gamma'(s)|_{g(\gamma(s))} = 1\Big\},
\end{equation*}
equipped with the norm $\|\cdot\|_{C^{k+2}([0,L])}$. Note that the norms involved in the Sobolev spaces are the Euclidean norms. Let $r\in\EN$. We define the space $\Theta^{r,k}(D)$ of angle distributions on $D$:
\begin{equation*}
  \Theta^{r,k}(D) = C^r\big([0,L_u],C^k([0,L_v], \R/2\pi\Z)\big),
\end{equation*}
equipped with the norm 
\begin{equation*}
  \|\omega\|_{\Theta^{r,k}(D)} = \|\omega\|_{C^r([0,L_u],C^k([0,L_v]))}.
\end{equation*}
 In the case where $k=r$, the notation of $\Theta^{k,k}(D)$ is simplified to $\Theta^k(D)$. We denote $\Phi^{r,k+2}(D)$ the closed subset of the Banach space $C^r([0,L_u],C^{k+2}([0,L_v],\surf))$ formed by arc-length parametrized curves with $C^{k+2}$-regularity depending on a parameter of regularity $C^r$:
\begin{equation*}  
  \Phi^{r,k+2}(D) := C^r\big([0,L_u], \Gamma^{k+2}([0,L_v])\big)\subset C^r\big([0,L_u],C^{k+2}([0,L_v],\surf)\big).
\end{equation*}
This space is equipped with the norm 
\begin{equation*}
  \|\varphi\|_{\Phi^{r,k+2}(D)} = \|\varphi\|_{C^r([0,L_u],\Gamma^{k+2}([0,L_v]))}.
\end{equation*}
 Note that we do not require the regularity on the first variable to be the same as the regularity on the second variable. This will be made visible in the construction of the candidate Chebyshev net $\varphi$: the first coordinate denotes the initial conditions of an ordinary differential equation in the second coordinate, which does not entail the same regularity.

Let $\gamma=(\gamma_u,\gamma_v)\in\Gamma^{r+2}([0,L_u])\Times \Gamma^{k+2}([0,L_v])$ be two curves with respective geodesic curvatures $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$, and such that $\gamma_u(0)=\gamma_v(0)$. We define the affine subspace composed of the angle distributions satisfying the boundary conditions \eqref{eq:cond-bord-angle}:
\begin{equation*}  
    \Theta_{\gamma}^{r,k}(D) =
    \left\{ 
      % \begin{array}{c|c} 
      \omega \in \Theta^{r,k}(D),
    % \begin{array}{l}
  %     \displaystyle\omega(u, 0) = \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\\
  %     \displaystyle\omega(0,v) = \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds
  %   \end{array}\\
  % \end{array}
\text{ s.t. $\omega$ satisfies \eqref{eq:cond-bord-angle}}\right\}.
\end{equation*}
The subspace $\Theta^{r,k}_{\gamma}$ is a closed subset of the Banach space $\Theta^{r,k}$. Again, in the case where $r=k$, we set $\Theta_{\gamma}^k=\Theta_{\gamma}^{k,k}$.

We can now restate Theorem \ref{thm2inexact} with the correct regularity.
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2}
Let $\surf$ be a smooth, open, complete, and simply connected surface and let $k\in\EN$. Let $\gamma=(\gamma_u,\gamma_v)\in\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])$, with $L_u,L_v\in\R_\ast^+$, be two curves with respective geodesic curvatures $\ko_u\in C^k([0,L_u])$ and $\ko_v\in C^k([0,L_v])$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose that $\angle(\gamma_1'(0),\gamma_2'(0))\in(0,\pi)$. Then, there exists a unique angle distribution $\omega:=\J(\gamma) \in \Theta^{k+1}_{\gamma}(D)$, with $D=[0,L_u]\Times[0,L_v]$, verifying the boundary conditions \eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)\in\Phi^{k+2}(D)$ the unique mapping satisfying \eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}.

Suppose moreover that we have $0<\omega(u,v)<\pi$, for all $(u,v)\in D$. Then, $\varphi$ is a Chebyshev net, i.e., it also satisfies \eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda}, and the mappings
\begin{equation*}
\begin{array}{cccc}
\J:&\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])&\to&\Theta^{k+1}(D),\\
  \I:&\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])\Times\Theta^{k+1}(D)&\to&\Phi^{k+2}(D)
\end{array}
\end{equation*}
are continuous.
\end{theorem}

@@

\section{Introduction}
We call {\em surface} a Riemannian 2-manifold, whose metric will be denoted $g$, and we consider complete, simply connected surfaces. 
A Chebyshev net $\varphi:U\subset\R^2\to\varphi(U)\subset\surf$, with $U$ an open set, is a coordinate system satisfying
\begin{equation}\label{eq:cheb-def}
  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v) = 1,
\end{equation}
for all $(u,v)\in U$.
We construct in what follows Chebyshev nets with a finite set of conical singularities on surfaces with finite total negative curvature and total positive curvature lower than $2\pi$. The main result of this section is the following theorem.
\begin{theorem}[Existence of piecewise smooth Chebyshev nets with singularities]\label{thm:existence-cheb-net}
  Let $\surf$ be a smooth, complete, simply connected surface satisfying
\begin{equation} \label{eq:cond-thm}
  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
\end{equation}
where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
Then, there exists a piecewise smooth Chebyshev net with conical singularities \sloppy$\CC=\big(\{\halfP^i_e\}_{1\leq i\leq \Npol}, \{\varphi^i_e\}_{1\leq i\leq \Npol}, T)$, with $\Npol\leq \frac{4}{\pi}\int_\surf K^-+8$, on $\surf$.
% $p_1,...,p_{\Nsing}$, with $\Nsing\leq N_{\max}$, of valence $n_1,...,n_{\Nsing}\in\{5,...,N_{\max}+4\}$ on $\surf$.
\end{theorem}
We highlight that the proof of the theorem is constructive. %Then, let us notice that the Chebyshev net with conical singularities constructed in Theorem \ref{thm:existence-cheb-net} induces a bi-Lipschitz mapping from the plane to $\surf$ \cite{Bur05}. As a result, this theorem is optimal for surfaces having a Gaussian curvature with constant sign \cite{Bonk03}.
The section is organized as follows. In Section \ref{subsec:Nhalf-surfaces}, we first consider the construction of Chebyshev nets on broken half-surfaces, defined to be half-surfaces with polygonal boundaries. We prove the existence of Chebyshev nets on broken half-surfaces under some condition on their total curvature in Theorem \ref{thm:cheb-half-surface}. Then, we show in Section \ref{subsec:splitting} that we can split surfaces satisfying \eqref{eq:cond-thm} into broken half-surfaces (Theorem \ref{thm:splitting-surf}), each of them satisfying the conditions of Theorem \ref{thm:cheb-half-surface}. Finally, we combine these two results to construct the Chebyshev net with conical singularities in Section \ref{subsec:cheb-net-sing} and we show that this Chebyshev net is piecewise smooth.

@@

\section{Proof of the main theorem}\label{subsec:cheb-net-sing}
We prove in this section Theorem \ref{thm:existence-cheb-net} on the existence of piecewise smooth Chebyshev nets with singularities on surfaces $\surf$ satisfying the curvature bound \eqref{eq:cond-thm}.
We first gather the results of Theorem  \ref{thm:cheb-half-surface} and Theorem \ref{thm:splitting-surf} to construct a Chebyshev net with singularities on $\surf$ (Theorem \ref{thm:exist-cheb-sing}). Then, we show that the Chebyshev parametrization obtained on each broken half-surface by Theorem \ref{thm:cheb-half-surface} is piecewise smooth (Theorem \ref{thm:cheb-half-surface-smooth3}). The proof of Theorem \ref{thm:existence-cheb-net} then follows from Theorem \ref{thm:exist-cheb-sing} and Theorem \ref{thm:cheb-half-surface-smooth3}.

>>>>

\modif{Théorème final}
\begin{theorem}[Existence of a smooth Chebyshev net out of a finite
    number of balls]\label{thm:main_thm}
  Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$ satisfying
\begin{equation} \label{eq:cond-thm}
  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
\end{equation}
where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
Then, there exists a finite number of balls $(\B_i)_{1\leq i\leq \N}$
with an arbitrary small radius $\varepsilon$ such that
$M\setminus\bigcup_{1\leq i\leq \N}\B_i$ admits a smooth Chebyshev
net. \modif{Ajouter estimation sur $\N$.}
\end{theorem}

@@

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:

\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2smooth}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be two smooth
curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega:D\to(0,\pi)$ verifying the boundary conditions
\eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula
\eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the
unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a smooth Chebyshev net on $\Omega$ with angles
$0<\omega<\pi$.
\end{theorem}

We in fact prove a slightly stronger version of Theorem
\ref{thm2smooth}. Denote $\Phi^{r,k} =
C^{r}([0,L_u],C^{k}([0,L_v],\R^2))$ the space of mappings of $D$ to
$\R^2$ with $C^r$ regularity in the first variable and $C^k$
regularity in the second variable. Similarly, define
$\Theta^{r,k}=C^r([0,L_u],C^k([0,L_v],\R))$ the space of real
functions on $D$ with $C^r$ regularity in the first variable and $C^k$
regularity in the second variable. To simplify notations, set
$\Phi^{k,k}=\Phi^k$ and $\Theta^{k,k}=\Theta^k$.

\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$k\in\mathbb{N}$. Let $\gamma_u:\R^+\to\surf$ and
$\gamma_v:\R^+\to\surf$ be two curves with $C^{k+2}$ regularity, with
respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega\in \Theta^{k+1}$ verifying the boundary
conditions \eqref{eq:cond-bord-angle} and satisfying the Hazzidakis
formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega):
D\to\surf$ the unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a Chebyshev net with $\Phi^{k+2}$ regularity on $\Omega$
with angles $0<\omega<\pi$.
\end{theorem}

\modif{Annonce du plan à retravailler}

In order to prove Theorem \ref{thm2}, we proceed along the following plan. In Section \ref{subsec:constr-param}, given the two curves $\gamma_u$ and $\gamma_v$ on $\surf$ and the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves, we first construct the candidate Chebyshev net $\varphi=\I(\gamma,\omega):D\to\surf$. We then show that whenever $\varphi$ satisfies the integrability condition \eqref{eq:cond-integr}, this mapping also satisfies \eqref{eq:cheb-def-c3} under suitable regularity conditions.  In Section \ref{subsec:exist-pt-fixe}, we view the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)$, as a fixed-point problem on $\omega$. We show existence and uniqueness of the solution to this fixed-point equation for the curves $\gamma_u$ and $\gamma_v\big|_{[0,L_0]}:[0,L_0]\to\surf$, where $L_0\in(0,L_v]$ is a constant depending on the $C^0$-norm of the geodesic curvatures of $\gamma_u$ and $\gamma_v$. This result is called ``local existence'' in what follows. We finally extend this result to the curves $\gamma_u$ and $\gamma_v$ of arbitrary length, in the spirit of the Cauchy--Lipschitz theorem.

%% \subsection{Functional spaces and statement of the main result}\label{sec:norms}

%% We now turn to the regularity required on the curves $\gamma_u$ and $\gamma_v$ and on the angle distribution $\omega$. In what follows, we define the spaces in which the curves, parametrizations and angles are constructed.  %When no confusion is possible, the mention of $L$, $L_u$ and $L_v$ will be dropped in the following notations for the sake of brevity.
%% Recall that
%% \begin{equation*}
%%   D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+.
%% \end{equation*}
%% Let $k\in\EN$ and $L\in(0,L_v]$. We consider the space $C^{k+2}([0,L],\surf)$ of curves $\gamma$ with general parametrizations on $\surf$ and such that the geodesic curvature of $\gamma$ has $C^{k}$-regularity. % The space $W^{k+2,p}$, endowed with the norm
%% % \begin{equation}\label{normphi}
%% %   \|\gamma\|_{W^{k+2,p}} = |\gamma(0)|+|\gamma'(0)| + \|\gamma''\|_{W^{k,p}([0,L])},
%% % \end{equation}
%% % is a Banach space.
%% We define $\Gamma^{k+2}([0,L])$ to be the closed subset of $C^{k+2}([0,L],\surf)$ formed by arc-length parametrized curves:
%% \begin{equation*}  
%%   \Gamma^{k+2}([0,L]) = \Big\{\gamma \in C^{k+2}([0,L], \surf) \text{ s.t. } \forall s\in[0,L],~ |\gamma'(s)|_{g(\gamma(s))} = 1\Big\},
%% \end{equation*}
%% equipped with the norm $\|\cdot\|_{C^{k+2}([0,L])}$. Note that the norms involved in the Sobolev spaces are the Euclidean norms. Let $r\in\EN$. We define the space $\Theta^{r,k}(D)$ of angle distributions on $D$:
%% \begin{equation*}
%%   \Theta^{r,k}(D) = C^r\big([0,L_u],C^k([0,L_v], \R/2\pi\Z)\big),
%% \end{equation*}
%% equipped with the norm 
%% \begin{equation*}
%%   \|\omega\|_{\Theta^{r,k}(D)} = \|\omega\|_{C^r([0,L_u],C^k([0,L_v]))}.
%% \end{equation*}
%%  In the case where $k=r$, the notation of $\Theta^{k,k}(D)$ is simplified to $\Theta^k(D)$. We denote $\Phi^{r,k+2}(D)$ the closed subset of the Banach space $C^r([0,L_u],C^{k+2}([0,L_v],\surf))$ formed by arc-length parametrized curves with $C^{k+2}$-regularity depending on a parameter of regularity $C^r$:
%% \begin{equation*}  
%%   \Phi^{r,k+2}(D) := C^r\big([0,L_u], \Gamma^{k+2}([0,L_v])\big)\subset C^r\big([0,L_u],C^{k+2}([0,L_v],\surf)\big).
%% \end{equation*}
%% This space is equipped with the norm 
%% \begin{equation*}
%%   \|\varphi\|_{\Phi^{r,k+2}(D)} = \|\varphi\|_{C^r([0,L_u],\Gamma^{k+2}([0,L_v]))}.
%% \end{equation*}
%%  Note that we do not require the regularity on the first variable to be the same as the regularity on the second variable. This will be made visible in the construction of the candidate Chebyshev net $\varphi$: the first coordinate denotes the initial conditions of an ordinary differential equation in the second coordinate, which does not entail the same regularity.

%% Let $\gamma=(\gamma_u,\gamma_v)\in\Gamma^{r+2}([0,L_u])\Times \Gamma^{k+2}([0,L_v])$ be two curves with respective geodesic curvatures $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$, and such that $\gamma_u(0)=\gamma_v(0)$. We define the affine subspace composed of the angle distributions satisfying the boundary conditions \eqref{eq:cond-bord-angle}:
%% \begin{equation*}  
%%     \Theta_{\gamma}^{r,k}(D) =
%%     \left\{ 
%%       % \begin{array}{c|c} 
%%       \omega \in \Theta^{r,k}(D),
%%     % \begin{array}{l}
%%   %     \displaystyle\omega(u, 0) = \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\\
%%   %     \displaystyle\omega(0,v) = \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds
%%   %   \end{array}\\
%%   % \end{array}
%% \text{ s.t. $\omega$ satisfies \eqref{eq:cond-bord-angle}}\right\}.
%% \end{equation*}
%% The subspace $\Theta^{r,k}_{\gamma}$ is a closed subset of the Banach space $\Theta^{r,k}$. Again, in the case where $r=k$, we set $\Theta_{\gamma}^k=\Theta_{\gamma}^{k,k}$.

%% We can now restate Theorem \ref{thm2inexact} with the correct regularity.
%% \begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2}
%% Let $\surf$ be a smooth, open, complete, and simply connected surface and let $k\in\EN$. Let $\gamma=(\gamma_u,\gamma_v)\in\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])$, with $L_u,L_v\in\R_\ast^+$, be two curves with respective geodesic curvatures $\ko_u\in C^k([0,L_u])$ and $\ko_v\in C^k([0,L_v])$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose that $\angle(\gamma_1'(0),\gamma_2'(0))\in(0,\pi)$. Then, there exists a unique angle distribution $\omega:=\J(\gamma) \in \Theta^{k+1}_{\gamma}(D)$, with $D=[0,L_u]\Times[0,L_v]$, verifying the boundary conditions \eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)\in\Phi^{k+2}(D)$ the unique mapping satisfying \eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}.

%% Suppose moreover that we have $0<\omega(u,v)<\pi$, for all $(u,v)\in D$. Then, $\varphi$ is a Chebyshev net, i.e., it also satisfies \eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda}, and the mappings
%% \begin{equation*}
%% \begin{array}{cccc}
%% \J:&\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])&\to&\Theta^{k+1}(D),\\
%%   \I:&\Gamma^{k+2}([0,L_u])\Times\Gamma^{k+2}([0,L_v])\Times\Theta^{k+1}(D)&\to&\Phi^{k+2}(D)
%% \end{array}
%% \end{equation*}
%% are continuous.
%% \end{theorem}

@@

\section{Introduction}
We call {\em surface} a Riemannian 2-manifold, whose metric will be denoted $g$, and we consider complete, simply connected surfaces. 
A Chebyshev net $\varphi:U\subset\R^2\to\varphi(U)\subset\surf$, with $U$ an open set, is a coordinate system satisfying
\begin{equation}\label{eq:cheb-def}
  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v) = 1,
\end{equation}
for all $(u,v)\in U$.
We construct in what follows Chebyshev nets with a finite set of conical singularities on surfaces with finite total negative curvature and total positive curvature lower than $2\pi$. The main result of this section is the following theorem.
\begin{theorem}[Existence of piecewise smooth Chebyshev nets with singularities]\label{thm:existence-cheb-net}
  Let $\surf$ be a smooth, complete, simply connected surface satisfying
\begin{equation} \label{eq:cond-thm2}
  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
\end{equation}
where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
Then, there exists a piecewise smooth Chebyshev net with conical singularities \sloppy$\CC=\big(\{\halfP^i_e\}_{1\leq i\leq \Npol}, \{\varphi^i_e\}_{1\leq i\leq \Npol}, T)$, with $\Npol\leq \frac{4}{\pi}\int_\surf K^-+8$, on $\surf$.
% $p_1,...,p_{\Nsing}$, with $\Nsing\leq N_{\max}$, of valence $n_1,...,n_{\Nsing}\in\{5,...,N_{\max}+4\}$ on $\surf$.
\end{theorem}
We highlight that the proof of the theorem is constructive. %Then, let us notice that the Chebyshev net with conical singularities constructed in Theorem \ref{thm:existence-cheb-net} induces a bi-Lipschitz mapping from the plane to $\surf$ \cite{Bur05}. As a result, this theorem is optimal for surfaces having a Gaussian curvature with constant sign \cite{Bonk03}.
The section is organized as follows. In Section \ref{subsec:Nhalf-surfaces}, we first consider the construction of Chebyshev nets on broken half-surfaces, defined to be half-surfaces with polygonal boundaries. We prove the existence of Chebyshev nets on broken half-surfaces under some condition on their total curvature in Theorem \ref{thm:cheb-half-surface}. Then, we show in Section \ref{subsec:splitting} that we can split surfaces satisfying \eqref{eq:cond-thm} into broken half-surfaces (Theorem \ref{thm:splitting-surf}), each of them satisfying the conditions of Theorem \ref{thm:cheb-half-surface}. Finally, we combine these two results to construct the Chebyshev net with conical singularities in Section \ref{subsec:cheb-net-sing} and we show that this Chebyshev net is piecewise smooth.

@@

\section{Proof of the main theorem}\label{subsec:cheb-net-sing}
We prove in this section Theorem \ref{thm:main_thm} on the existence of piecewise smooth Chebyshev nets with singularities on surfaces $\surf$ satisfying the curvature bound \eqref{eq:cond-thm}.
We first gather the results of Theorem  \ref{thm:cheb-half-surface} and Theorem \ref{thm:splitting-surf} to construct a Chebyshev net with singularities on $\surf$ (Theorem \ref{thm:exist-cheb-sing}). Then, we show that the Chebyshev parametrization obtained on each broken half-surface by Theorem \ref{thm:cheb-half-surface} is piecewise smooth (Theorem \ref{thm:cheb-half-surface-smooth3}). The proof of Theorem \ref{thm:main_thm} then follows from Theorem \ref{thm:exist-cheb-sing} and Theorem \ref{thm:cheb-half-surface-smooth3}.
